Co-moving stars in \textsl{Gaia DR1}:\\ An abundance of very wide separation co-moving pairs

### 2017-02-14 paper/table_meta.tex
new catalog

\begin{table}[htb]
\centering
\caption{Candidate co-moving pairs catalog description} \label{tab:table_meta}
\begin{tabular}{l|l|l}
\hline\hline
Column                                & Unit   & Description                         \\
\hline
\multicolumn{3}{c}{Table: Star (10,606 rows)}                                         \\
\hline
row id                                &        & zero-based row index                \\
TGAS source id                        &        & unique source id from \tgas          \\
RA                         & deg       & right ascension from \tgas          \\
DEC                        & deg       & declination from \tgas          \\
parallax                       & mas     & unique source id from \tgas          \\
distance                       & pc     & unique source id from \tgas          \\
$G$                               & mag    & \gaia\ $G$-band magnitudes            \\
$J$                               & mag    & \tmass\ $J$-band magnitudes            \\
$H$                               & mag    & \tmass\ $H$-band magnitudes            \\
RAVE OBS ID                           &        & unique id of the \rave\ match            \\
RV                                    & \kms   & radial velocity from \rave\           \\
eRV                                   & \kms   & uncertainty of radial velocity from \rave            \\
group id & & Id of the group this star belongs to\\
\hline
\multicolumn{3}{c}{Table: Pair (13,058 rows)}                                            \\
\hline
angsep                                & arcmin & angular separation                  \\
separation                            & pc     & physical separation                 \\
$\ln\mathcal{L}_1/\mathcal{L}_2$ &        & likelihood ratio                    \\
group id                              &        & id of the group the pair belongs to \\
\hline
\multicolumn{3}{c}{Table: Group (4,555 rows)}                                         \\
\hline
id                                    &        & unique group id                     \\
size                                  &        & number of stars in a group          \\
                                      &        &                                     \\
\hline\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htb]
\centering
\caption{Candidate co-moving pairs catalog description} \label{tab:table_meta}
\begin{tabular}{l|l|l}
\hline\hline
Column Name    & Unit & Description                         \\
\hline
\multicolumn{3}{c}{Table: Star (10,606 rows)}                                         \\
\hline
row id         &      & zero-based row index                      \\
TGAS source id &      & unique source id from \tgas               \\
RA             & deg  & right ascension from \tgas                \\
DEC            & deg  & declination from \tgas                    \\
parallax       & mas  & unique source id from \tgas               \\
distance       & pc   & unique source id from \tgas               \\
$G$            & mag  & \gaia\ $G$-band magnitudes                \\
$J$            & mag  & \tmass\ $J$-band magnitudes               \\
$H$            & mag  & \tmass\ $H$-band magnitudes               \\
RAVE OBS ID    &      & unique id of the \rave\ match             \\
RV             & \kms & radial velocity from \rave\               \\
eRV            & \kms & uncertainty of radial velocity from \rave \\
group id       &      & Id of the group this star belongs to      \\
\hline
\multicolumn{3}{c}{Table: Pair (13,058 rows)}                                            \\
\hline
angsep                           & arcmin & angular separation                  \\
separation                       & pc     & physical separation                 \\
$\ln\mathcal{L}_1/\mathcal{L}_2$ &        & likelihood ratio                    \\
group id                         &        & id of the group the pair belongs to \\
\hline
\multicolumn{3}{c}{Table: Group (4,555 rows)}                                         \\
\hline
id     &        & unique group id                     \\
size   &        & number of stars in a group          \\
       &        &                                     \\
\hline\hline
\end{tabular}
\end{table}
